
% 300- words total
% 50- words per argument, 4-6 arguments
\section{Others' Arguments}

% EPA engineers were at fault, their tests were poorly designed\cite{epa_track}.
\subsection{Poorly Designed Tests}
EPA engineers \textbf{were} in violation of the Software Engineering Code of Ethics. They violated the code by designing tests that were easy to exploit. It is their fault that VW was able to implement a defeat device to beat their tests\cite{epa_track}.

% EPA engineers were not at fault, it was VW's responsibility to remain honest\cite{vw_ethics}.
\subsection{VW Honesty}
EPA engineers \textbf{were not} in violation of the Software Engineering Code of Ethics. Although their engineers failed to design tests that VW was incapable of beating, it was the responsibility of VW's engineers to remain honest. VW's engineers were the ones to violate the SE Code\cite{vw_ethics}.

% EPA engineers were not at fault, they were required to release a large amount of their testing procedures, allowing VW to take advantage\cite{vw_ethics}.
\subsection{Too Much Transparency}
EPA engineers \textbf{were not} in violation of the Software Engineering Code of Ethics. Because of legislation regarding transparency in the government, EPA engineers were required to release a large amount of information regarding the testing environment. EPA's engineers were not able to prevent VW from cheating, as legislation prevented them from doing so\cite{vw_ethics}.
% Furthermore, the EPA's engineers could not have been expected to act outside of the law 'for the greater good', as they had no means of predicting that cheating would occur.

% EPA engineers were not at fault, VW's exploits were highly complex\cite{cheating_analysis}.
\subsection{Too Little Transparency}
EPA engineers \textbf{were not} in violation of the Software Engineering Code of Ethics. Because of legislation regarding transparency in the auto industry, EPA engineers were not given the resources to adequately test automobiles for emissions compliance. VW's defeat device was more complex than EPA engineers were prepared or able to test for\cite{cheating_analysis}.